---
title: "Data Hygiene E2"
author: "Ana Baciero"
date: "April 19, 2018"
output:
  html_document:
    df_print: paged
---
# Data quality plan

1. Every subject should have done the same amount of trials.
2. The accuracy for each subject should be above 50%.
3. RTs for each trial should be higher than 200 ms.
4. RTs for each trial should be lower than 15000 ms.

5. Every pair must have at least 15 responses.


```{r}
library(tidyverse)
library(dplyr)
library(knitr)
library(smacof)
library(pmr)
library(shape)
library(gplots)
library(RColorBrewer)
library(rafalib)
library(dendextend)
```

#Experiment2: Data Set
```{r}

Participant<-rep(1:84,each=260)

E2.P1.rw<- read.delim(as.character("P1"),header = T)
E2.P1<- E2.P1.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P2.rw<- read.delim(as.character("P2"),header = T)
E2.P2<- E2.P2.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P3.rw<- read.delim(as.character("P3"),header = T)
E2.P3<- E2.P3.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P4.rw<- read.delim(as.character("P4"),header = T)
E2.P4<- E2.P4.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P5.rw<- read.delim(as.character("P5"),header = T)
E2.P5<- E2.P5.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P6.rw<- read.delim(as.character("P6"),header = T)
E2.P6<- E2.P6.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P7.rw<- read.delim(as.character("P7"),header = T)
E2.P7<- E2.P7.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P8.rw<- read.delim(as.character("P8"),header = T)
E2.P8<- E2.P8.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P9.rw<- read.delim(as.character("P9"),header = T)
E2.P9<- E2.P9.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P10.rw<- read.delim(as.character("P10"),header = T)
E2.P10<- E2.P10.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P11.rw<- read.delim(as.character("P11"),header = T)
E2.P11<- E2.P11.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P12.rw<- read.delim(as.character("P12"),header = T)
E2.P12<- E2.P12.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P13.rw<- read.delim(as.character("P13"),header = T)
E2.P13<- E2.P13.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P14.rw<- read.delim(as.character("P14"),header = T)
E2.P14<- E2.P14.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P15.rw<- read.delim(as.character("P15"),header = T)
E2.P15<- E2.P15.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P16.rw<- read.delim(as.character("P16"),header = T)
E2.P16<- E2.P16.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P17.rw<- read.delim(as.character("P17"),header = T)
E2.P17<- E2.P17.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P18.rw<- read.delim(as.character("P18"),header = T)
E2.P18<- E2.P18.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P19.rw<- read.delim(as.character("P19"),header = T)
E2.P19<- E2.P19.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P20.rw<- read.delim(as.character("P20"),header = T)
E2.P20<- E2.P20.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P21.rw<- read.delim(as.character("P21"),header = T)
E2.P21<- E2.P21.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P22.rw<- read.delim(as.character("P22"),header = T)
E2.P22<- E2.P22.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P23.rw<- read.delim(as.character("P23"),header = T)
E2.P23<- E2.P23.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P24.rw<- read.delim(as.character("P24"),header = T)
E2.P24<- E2.P24.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P25.rw<- read.delim(as.character("P25"),header = T)
E2.P25<- E2.P25.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P26.rw<- read.delim(as.character("P26"),header = T)
E2.P26<- E2.P26.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P27.rw<- read.delim(as.character("P27"),header = T)
E2.P27<- E2.P27.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P28.rw<- read.delim(as.character("P28"),header = T)
E2.P28<- E2.P28.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P29.rw<- read.delim(as.character("P29"),header = T)
E2.P29<- E2.P29.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P30.rw<- read.delim(as.character("P30"),header = T)
E2.P30<- E2.P30.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P31.rw<- read.delim(as.character("P31"),header = T)
E2.P31<- E2.P31.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P32.rw<- read.delim(as.character("P32"),header = T)
E2.P32<- E2.P32.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P33.rw<- read.delim(as.character("P33"),header = T)
E2.P33<- E2.P33.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P34.rw<- read.delim(as.character("P34"),header = T)
E2.P34<- E2.P34.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P35.rw<- read.delim(as.character("P35"),header = T)
E2.P35<- E2.P35.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P36.rw<- read.delim(as.character("P36"),header = T)
E2.P36<- E2.P36.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P37.rw<- read.delim(as.character("P37"),header = T)
E2.P37<- E2.P37.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P38.rw<- read.delim(as.character("P38"),header = T)
E2.P38<- E2.P38.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P39.rw<- read.delim(as.character("P39"),header = T)
E2.P39<- E2.P39.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P40.rw<- read.delim(as.character("P40"),header = T)
E2.P40<- E2.P40.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)
E2.P43.rw<- read.delim(as.character("P43"),header = T)
E2.P43<- E2.P43.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P44.rw<- read.delim(as.character("P44"),header = T)
E2.P44<- E2.P44.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P45.rw<- read.delim(as.character("P45"),header = T)
E2.P45<- E2.P45.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P46.rw<- read.delim(as.character("P46"),header = T)
E2.P46<- E2.P46.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P47.rw<- read.delim(as.character("P47"),header = T)
E2.P47<- E2.P47.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P48.rw<- read.delim(as.character("P48"),header = T)
E2.P48<- E2.P48.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P49.rw<- read.delim(as.character("P49"),header = T)
E2.P49<- E2.P49.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P50.rw<- read.delim(as.character("P50"),header = T)
E2.P50<- E2.P50.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P51.rw<- read.delim(as.character("P51"),header = T)
E2.P51<- E2.P51.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P52.rw<- read.delim(as.character("P52"),header = T)
E2.P52<- E2.P52.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P53.rw<- read.delim(as.character("P53"),header = T)
E2.P53<- E2.P53.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P54.rw<- read.delim(as.character("P54"),header = T)
E2.P54<- E2.P54.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P55.rw<- read.delim(as.character("P55"),header = T)
E2.P55<- E2.P55.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P56.rw<- read.delim(as.character("P56"),header = T)
E2.P56<- E2.P56.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P57.rw<- read.delim(as.character("P57"),header = T)
E2.P57<- E2.P57.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P58.rw<- read.delim(as.character("P58"),header = T)
E2.P58<- E2.P58.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P59.rw<- read.delim(as.character("P59"),header = T)
E2.P59<- E2.P59.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P60.rw<- read.delim(as.character("P60"),header = T)
E2.P60<- E2.P60.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P61.rw<- read.delim(as.character("P61"),header = T)
E2.P61<- E2.P61.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P62.rw<- read.delim(as.character("P62"),header = T)
E2.P62<- E2.P62.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P63.rw<- read.delim(as.character("P63"),header = T)
E2.P63<- E2.P63.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P64.rw<- read.delim(as.character("P64"),header = T)
E2.P64<- E2.P64.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P65.rw<- read.delim(as.character("P65"),header = T)
E2.P65<- E2.P65.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P66.rw<- read.delim(as.character("P66"),header = T)
E2.P66<- E2.P66.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P67.rw<- read.delim(as.character("P67"),header = T)
E2.P67<- E2.P67.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P68.rw<- read.delim(as.character("P68"),header = T)
E2.P68<- E2.P68.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P69.rw<- read.delim(as.character("P69"),header = T)
E2.P69<- E2.P69.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P70.rw<- read.delim(as.character("P70"),header = T)
E2.P70<- E2.P70.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P71.rw<- read.delim(as.character("P71"),header = T)
E2.P71<- E2.P71.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P72.rw<- read.delim(as.character("P72"),header = T)
E2.P72<- E2.P72.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P73.rw<- read.delim(as.character("P73"),header = T)
E2.P73<- E2.P73.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P74.rw<- read.delim(as.character("P74"),header = T)
E2.P74<- E2.P74.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P75.rw<- read.delim(as.character("P75"),header = T)
E2.P75<- E2.P75.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P76.rw<- read.delim(as.character("P76"),header = T)
E2.P76<- E2.P76.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P77.rw<- read.delim(as.character("P77"),header = T)
E2.P77<- E2.P77.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P78.rw<- read.delim(as.character("P78"),header = T)
E2.P78<- E2.P78.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P79.rw<- read.delim(as.character("P79"),header = T)
E2.P79<- E2.P79.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P80.rw<- read.delim(as.character("P80"),header = T)
E2.P80<- E2.P80.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P81.rw<- read.delim(as.character("P81"),header = T)
E2.P81<- E2.P81.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P82.rw<- read.delim(as.character("P82"),header = T)
E2.P82<- E2.P82.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P83.rw<- read.delim(as.character("P83"),header = T)
E2.P83<- E2.P83.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P84.rw<- read.delim(as.character("P84"),header = T)
E2.P84<- E2.P84.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P85.rw<- read.delim(as.character("P85"),header = T)
E2.P85<- E2.P85.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)

E2.P86.rw<- read.delim(as.character("P86"),header = T)
E2.P86<- E2.P86.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(7:266)


Data.rw.E2<- rbind(E2.P1, E2.P2, E2.P3, E2.P4, E2.P5, E2.P6, E2.P7, E2.P8, E2.P9, E2.P10, E2.P11, E2.P12, E2.P13, E2.P14, E2.P15, E2.P16, E2.P17, E2.P18, E2.P19, E2.P20, E2.P21, E2.P22, E2.P23, E2.P24, E2.P25, E2.P26, E2.P27, E2.P28, E2.P29, E2.P30, E2.P31, E2.P32, E2.P33, E2.P34, E2.P35, E2.P36, E2.P37, E2.P38, E2.P39, E2.P40, E2.P43, E2.P44, E2.P45, E2.P46, E2.P47, E2.P48, E2.P49, E2.P50, E2.P51, E2.P52, E2.P53, E2.P54, E2.P55, E2.P56, E2.P57, E2.P58, E2.P59, E2.P60, E2.P61, E2.P62, E2.P63, E2.P64, E2.P65, E2.P66, E2.P67, E2.P68, E2.P69, E2.P70, E2.P71, E2.P72, E2.P73, E2.P74, E2.P75, E2.P76, E2.P77, E2.P78, E2.P79, E2.P80, E2.P81, E2.P82, E2.P83, E2.P84, E2.P85, E2.P86)
Data.rw.E2<-cbind(Participant,Data.rw.E2)
Data.rw.E2<- Data.rw.E2%>% 
  mutate(rubric = if_else(IT1==IT2,1,0))%>%
  mutate(accuracy = if_else(Key =="m" & rubric == "1", 1,
                            if_else(Key == "n" & rubric == "0",1,0)))%>%
  mutate(RT=as.numeric(RT))

```

# More participants
```{r}
P<- as.data.frame(rep(85:87, each=210))
colnames(P)<-c("Participant")

E2.P87.rw<- read.delim(as.character("P87"),header = T)
E2.P87<- E2.P87.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(6:215)
E2.P88.rw<- read.delim(as.character("P88"),header = T)
E2.P88<- E2.P88.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(6:215)
E2.P89.rw<- read.delim(as.character("P89"),header = T)
E2.P89<- E2.P89.rw%>%
  separate(IT1.IT2.KEY.RT,  c("a","b","c","d","e","IT1","IT2","f","g","h","i","j","k","Key","RT","miss"), sep = " ")%>%
  select("IT1","IT2","Key", "RT","miss")%>%
  slice(6:215)

Data.moreE2.rw<- rbind(E2.P87,E2.P88,E2.P89)
                     
Data.moreE2.rw<-cbind(P,Data.moreE2.rw)
Data.moreE2.rw<- Data.moreE2.rw%>% 
  mutate(rubric = if_else(IT1==IT2,1,0))%>%
  mutate(accuracy = if_else(Key =="m" & rubric == "1", 1,
                            if_else(Key == "n" & rubric == "0",1,0)))%>%
  mutate(RT=as.numeric(RT))


```

# THE DATA SET

```{r}

All.E2.rw<- rbind.data.frame(Data.rw.E2,Data.moreE2.rw)

```


## 1. Every subject should have done the same amount of trials:

```{r}

table(All.E2.rw$Participant)

# No NA values (2 key presses)

Data.analysis.E2<- All.E2.rw %>%
 select(Participant,IT1, IT2, Key, rubric, accuracy, RT)%>%
 na.omit()

table(Data.analysis.E2$Participant)

## Removed 22 observations (22470 - 22448)
```


## 2. The accuracy for each subject should be above 50%:
```{r}

Data.acc.E2<-Data.analysis.E2%>%
  select(Participant,accuracy)%>%
  group_by(Participant)%>%
  summarise_if(is.numeric,mean)

Data.acc.E2<.5


# Remove #44,65,67,75,87

Data.analysis.E2<- Data.analysis.E2%>%
  mutate(delete = if_else(Participant=="44",0,
                          if_else(Participant=="65",0,
                                  if_else(Participant=="67",0,
                                          if_else(Participant=="75",0,
                                                  if_else(Participant=="87",0,1))))))%>%
  filter(delete==1)%>%
  select(Participant,IT1, IT2, Key, rubric, accuracy, RT)

Data.acc.E2<-Data.analysis.E2%>%
  select(Participant,accuracy)%>%
  group_by(Participant)%>%
  summarise_if(is.numeric,mean)

Data.acc.E2<.5

mean(Data.acc.E2$accuracy)

#Removed 1246 observations (22448 - 21202)

```


## 3. RTs for each trial should be higher than 200 ms.
```{r}

Data.RT.E2.02<-Data.analysis.E2%>%
  select(RT)%>%
  filter(RT<0.2)

Data.RT.E2.10<-Data.analysis.E2%>%
  select(RT)%>%
  filter(RT>15)


Data.analysis.E2<-Data.analysis.E2%>%
  filter(RT>0.2)%>%
  filter(RT<15)

# Removed 157 observations (21202 - 21045)

```

## 4. Every pair must have at least 15 responses.

```{r}
Data.diffE2<-Data.analysis.E2%>%
  filter(rubric=="0")%>%
  select(IT1,IT2,Key)%>%
  group_by(IT1,IT2)%>%
  count

FewResponsesE2<- Data.diffE2%>%
  filter(n<15)
```


## Clean Data Set

```{r}

write_csv(Data.analysis.E2, path = "CleanData.E2_v2.csv", col_names = T)

```


########################################3
#More participants' list


```{r}
stim.1 <- letters
stim.2 <- letters
pair <- array(dim=26*26)
type <- array(dim = 26*26)

for(i in 1:26){
  for(j in 1:26){
    if (stim.1[i] == stim.2[j]) {
      type [(i-1)*26+j] <- 0
    }
    else {
      type[(i-1)*26+j] <- 1
    }
    pair[(i-1)*26+j] <- paste(stim.1[i], stim.2[j])
  }
}

type <- as.character(type)
pairs <- as.character(pair)
all<- as.data.frame(cbind(pairs, type))

same.rw<- all%>%
  select(pairs)%>%
  filter(type==0)

same.rw<- as.data.frame(paste("    ",same.rw$pairs,"    "))
same.rw<- as.data.frame(same.rw)

same.130 <- rbind(same.rw,same.rw,same.rw, same.rw,same.rw)
colnames(same.130)<- c("stimuli")

same <- as.character(sample(same.130$stimuli, 105, replace = F))
same<- as.data.frame(same)
colnames(same)<-c("stimuli")
different <- as.data.frame(paste(FewResponsesE2$IT1, FewResponsesE2$IT2))
colnames(different)<-c("stimuli")
different<- as.data.frame(paste("    ",different$stimuli,"    "))
colnames(different)<-c("stimuli")

New<- rbind.data.frame(same,different)
New.random<- as.data.frame(sample(New$stimuli))
colnames(New.random)<-c("stimuli")
Practice <- as.data.frame (c("h n","d d", "n r", "p z", "x x"))
colnames(Practice)<- c("stimuli")
Practice<- as.data.frame(paste("    ",Practice$stimuli,"    "))
colnames(Practice)<-c("stimuli")

NewList<- rbind.data.frame(Practice,New.random)

write.table(NewList,file ="LN2.txt", row.names = F, col.names = F, quote = F)

```


```
